%!TEX root=paper.tex

\section{Introduction}
% \ml{still too ``brainstormy''... }
% language learning - which in itself is a very broad issue with the potential to impact the lives of a very large number of people: 
At any given moment, numerous people are learning new languages. 
Only English, estimates the British Council, will be learned by two billion people by 2020. 
Although a plethora of tools and techniques exist for beginners, few exist to support the intermediates and advanced learners. for whom one of the best possible activities is extensive reading
% , since reading acts as a microcosm for all the other skills 
\cite{Day98-Extensive,mccarthy1999-extensive,mccarthy1999-microcosm}. 

% However, to enjoy the benefits of free reading, the learner must already be sufficiently fluent in the target language: even knowing 95\% of the vocabulary in a text, a learner still has to look up in average a word on every line. \cite{Hirsh92-vocab-size} This means that not any text is good for reading. Randomly choosing a text might actually end up being frustrating because the learner has to look up a lot of words in the dictionary.

However, when reading in a foreign language, most of the intermediate learners still require language textbooks. Such textbooks are designed by experts who make sure that the texts are simple enough for the desired language level of a broad audience and that exercises that allow the readers to practice newly learned concepts acompany the texts. 
% Texbooks are artefacts of the last century that did not change much over the years. 
In spite of becoming more colorful, being sold with complementary audio or video lessons, their main limitation remains unchanged since the last century: 
% static nature has not changed.
% essence they still are a collection of texts with associated exercises.
% We believe that one of the main limitations of the textbook approach stems from the fact that textbooks 
by being designed for a average learner they are not exciting for any individual learner \cite{Hidi00-TheUnmotivated}. A student interested in sports might not be motivated to read about {\em Maria who is a babysitter in Spain}. 
% 
The lack of motivation, a well known problem, especially with young learners \cite{Hidi00-TheUnmotivated,renadya07-power}, might be solved if learners could read materials that are personally interesting. If they would spend more time reading, their capabilities would increase, and enjoyment would result in further reading, in a virtuous circle \cite{Brozo07-Engagement, Guthrie99-Motivation}.

% As the US Air Force learned the hard way sixty years ago, ``there is no average pilot'': when cockpits, jumpsuits, and instructions were designed for the {\em average pilot}, the actual pilots had a hard time maneuvering the planes; performance improved only when the cockpit was designed in such a way as to be adjustable to the individual. 
% As a result, the motivation of the individual student for using textbooks is low. 

% The fact that textbooks do not work that well is illustrated also by the fact that some of the teachers of foreign languages whom we have spoken to, do not even use a textbook anymore, but instead find articles that they deem interesting online and share them with their students. Note that this could be a step in the right direction, since the teacher has a better understanding of the interests of the class. However, in the end, the student is still not reading what they are passionate about, but rather, what the teacher deems relevant. 

Given the vast amounts of multi-language content available and added daily on the Internet (e.g. blogs, news articles, eBooks) it is likely that every student can find materials that are {\em personally interesting} for them in almost any language they are learning. 
This would fit a general trend where old systems designed for the average user are being replaced with personalized attention across domains: in medicine\footnote{The nascent discipline of {\em personalized medicine} suggests that analysis of the genetic makeup of an individual may guide health care decisions far more precisely than big group studies do}, computer security,  web design \cite{Reinecke13-CulturalAdaptation}, or mathematical education \cite{Polozov15-AdaptableMath}. 
% 
% 
% The texts that one can read are limited to generic topics, which must appeal to the entire audience. Unfortunately a text that is good enough for everybody is likely not exciting for anybody. This limits the amount of reading that learners will do, and thus, limits their learning.
% 
% If there was a way to allow every reader to find and study materials that are interesting for them the motivation of the students would be highly increased. People could even 
% 
% 
% 
% 


Although individual components have been proposed before for free reading (e.g. browser extensions) and interactive exercises (e.g. Duolingo), a system that integrates free reading with personalized exercises into a {\em personalized textbook} has not been evaluated. The first contribution of this paper is describing the architecture and user experience of a system which combines: 

\begin{enumerate}
	
  \item {\bf Reading comprehension support on both desktop and mobile devices for texts that are interesting to the user.} If ideal comprehension support should work {\em ``without requiring even a single click''} \cite{Proszeky02-Comprehension}, the next best thing is one-click (or one-touch) support. This is combined with a system for estimating text difficulty that allows the learner to choose articles that are within their capabilities\footnote{This to address the problem of a learner chosing an article randomly from a website and discovering that it is too difficult and giving up. 
  % E.g. The articles in the {\em Neue Z\"uricher Zeitung} have a very high degree of difficulty variability: some can be read by beginners and some are be too difficult for intermediates.
  }.
  % Any interaction more complicated than this (e.g. opening an external dictionary) will interrupt the flow of the student.

  \item {\bf Integration between vocabulary practice and reading history.} Instead of manually adding words to an external vocabulary practice system, the most relevant unknown words encountered in the readings are automatically scheduled for practice, when possible in the context of the original text, since learning a word in context is more effective \cite{nagy95-context}.
  % TODO: on both mobile and desktop platforms

\end{enumerate}

The second contribution is the evaluation of the usefulness and usability of such a system by  deploying it with three classes of French learning highschool students for one month. We analyze their usage of the system, their feedback, and the feedback of their teacher to understand when and how such a system fits the modern language classroom.

% In the remainder of the paper we discuss the related work, present our system, present an exploratory analysis of the usage of the system in an in-the-wild sutdy with three higschool classes for one month. 
 % paper we propose a system that illustrates how the goal of using the web as the source for a personalized language textbook can be achieved.

% In this paper we are focusing our attention on a subset of education - 


% In order to address these three problems, we propose an infrastructure which allows learners to: 

% 	\begin{description}
	
% 		\item [Exert agency over the materials they study] by selecting written content that are interesting for them
	
% 		\item [Access conveniently translations for unknown words] in those cases when they are encountered, as it is unlikely that these words can be completely avoided.

% 		\item [Practice using personalized \& contextual exercises] that are generated automatically based on their past readings.

% 	\end{description}

% Although it is not the focus of this paper, the infrastructure should also Estimate the difficulty of a text in order to allow the learners to avoid materials that are too difficult. \ml{maybe don't even mention this... we're setting ourselves up for too much}

% In the remainder of this paper we describe the design of such a system (Section \ref{sec:system}) and we present our results from deploying the system for one month with a group of \students Dutch high school French learning students (Sections \ref{sec:demographics} -- \ref{sec:perception}). We then talk about the limitations of this study (Section \ref{sec:limitations}) and then we list some of the challenges that we think our infrastructure and similar ones must face in order to increase the chance of their acceptance in practice (Section \ref{sec:challenges}).

