%!TEX root=paper.tex

\newpage
\section{The Testing Environment}

\subsection{The Students}
The population that we tested our infrastructure with represent \stcnt highschool students from Groningen in the Netherlands. Their native language is Dutch and most of them speak fluent English. 


There are 54 female and 15 male with ages below 18 representing three different classes. Based on their own self characterization, 53 students are level B1 (Intermediate. Can understand the main points of clear standard speech. Can narrate an event, an experience or a dream.) and 16 are level A2 (Elementary. Using simple words, can describe his or her surroundings and communicate immediate needs). 


When asked whether they have topics half of the students mentioned some topics that they would rather prefer to read about, and the other half did not answer the question. From the topics that they listed as possible interests some of the more popular were: sports, music, travel, lifestyle, fashion, movies, and "no politics".


\subsection {The Rules of the Game}

At the begining of June, we visited the school, and we introduced the
way the infrastructure is to be used during one hour for each of the three participating classes.


The system was used for approximatively three weeks in June from the begining of the second week until the end of the month. All the students created account before June 9th. 

The teacher asked the students to be using the infrastructure and write reports on the way they used. For evey half an hour of usage, the students would have to write a brief report that they would submit to the teacher about how they spent their time. The teacher could then decide to selectively test them on the basis of their self-reported activity cards.

We deployed the system with the translations in English instead of Dutch and we made it clear to the students that if for some of them this is insufficient, they can ask us, and we will modify their personal account to Dutch. However, none of the students requested this.






% To talk to Nienke about the other types of analysis we can do on this data